---
title: "Birthday"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Birthday}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753F25landon)
```


# Question 1

We want the probability that in a group of size n, at least two people share the same birthday

\[ P(\text{all distinct}) = \frac{365}{365} \times \frac{364}{365} \times \cdots \times \frac{365-n+1}{365}. \]
 
 This can be written as
 
\[ P(\text{all distinct}) = \frac{365!}{(365-n)! \, 365^n}. \]

Therefore,

\[ P(\text{at least one match}) = 1 - \frac{365!}{(365-n)! \, 365^n}. \]
 
# Question 2

Using lfactorial and lchoose,

\[
P(\text{at least one match}) \;=\; 1 - \exp\!\Big( \texttt{lchoose(365, n)} + \texttt{lfactorial(n)} - n \log(365) \Big).
\]
 
  
# Question 3
```{r}
birthday
```

# Question 4
```{r}
birthday(20:25)
```
